A graph-based data model for interactive evolutionary computation

### 2017-01-20 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Spell check
Added references

  \item {\bf User-Individual}
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection [cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals [cite ES-I].

  \item {\bf User-User}
  Relationship between users can also be modeled 
  as a social network, with well established semantics, algorithms and metrics (cite).
  A graph model could enable researchers to find other ways of identifying leaders of 
  opinion or measuring the similarity between user's preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users' preferences.

@@

These relations are naturally mapped to graphs, while other actions and 
properties can also be modeled as a semantic network using
basic subject–-predicate-–object expressions [cite Semantic triples].
Another reason for using a graph model is the tools available for
implementing and query the model, and the increased performance of
native graph database systems [cite Christian].

@@

 \section{IEC Human-centered framework}
\label{sec:graph}
The general goal of this research is to develop a human-centered [cite] framework
for interactive evolutionary computation (IEC) in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given IEC application. We deliberately use the 
more general
term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. In other cases the evaluation could be done
by the natural interactions of a group of humans in a collaborative fashion
or not. For instance the IEC algorithm could by trying to optimize 
the design of an exit sign in an airport, then the quality of this sign could be
determined by the average the time it takes a sample of people to 
find the exit. In this example there could be certain collaboration
between users if they are not traveling alone, of course this is only one of
the considerations designers could make.

@@

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with individuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physically created
  the new population.  
\end{itemize}

@@

The score achieved by users depends on the actions he does in the system as
each time a user does one of these actions their score is incremented by one.
The actions considered in this application are: 
\begin{itemize}
\item Start a session.
\item Rate an individual.
\item Create a collection.
\item Save an individual of the wall to a collection.
\item Save an individual from a friend's collection.
\item Explore collections of other friends.
\end{itemize}
Only the "Start a session" and "Explore collections of other friends". 
Are not found in the graph model, 
%% Note: I must ask Christian where they are stored 
%%

The weight of the preference of a users can depend on two scores:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100.

@@

The comparation consisted on three versions:
\begin{itemize}
\item Non Gamification. All users have the same weight.
\item Non Graph Gamification. Only experience is considered
\item Graph Gamification. Both experience and participation where considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.

>>>>

  \item {\bf User-Individual}
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection \cite{Prodromou:16:AS}. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals \cite{garcia2013evospace}.

  \item {\bf User-User}
  Relationship between users can also be modeled 
  as a social network, with well established semantics, algorithms and metrics \cite{ahuja1993network}.
  A graph model could enable researchers to find other ways of identifying leaders of 
  opinion or measuring the similarity between user's preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users' preferences.

@@

These relations are naturally mapped to graphs, while other actions and 
properties can also be modeled as a semantic network using
basic subject–-predicate-–object expressions \cite{Prud'hommeaux:14:RT}.
Another reason for using a graph model is the tools available for
implementing and query the model, and the increased performance of
native graph database systems \cite{holzschuher2013performance,holzschuher2016querying}.

@@

 \section{IEC Human-centered framework}
\label{sec:graph}
The general goal of this research is to develop a human-centered \cite{gasson2003human} framework
for interactive evolutionary computation (IEC) in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given IEC application. We deliberately use the 
more general
term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. In other cases the evaluation could be done
by the natural interactions of a group of humans in a collaborative fashion
or not. For instance the IEC algorithm could by trying to optimize 
the design of an exit sign in an airport, then the quality of this sign could be
determined by the average the time it takes a sample of people to 
find the exit. In this example there could be certain collaboration
between users if they are not traveling alone, of course this is only one of
the considerations designers could make.

@@

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals
  from
  the population. There are many ways in which humans could interact 
  with individuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{merelo2016performance}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

@@

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project \cite{de2013unplugging} artists physically created
  the new population.  
\end{itemize}

@@

The score achieved by users depends on the actions he does in the system as
each time a user does one of these actions their score is incremented by one.
The actions considered in this application are: 
\begin{itemize}
\item Start a session.
\item Rate an individual.
\item Create a collection.
\item Save an individual of the wall to a collection.
\item Save an individual from a friend's collection.
\item Explore collections of other friends.
\end{itemize}
Only the "Start a session" and "Explore collections of other friends". 
Are not found in the graph model, 
%% Note: I must ask Christian where they are stored 
%%
Two scores are used to determine the weight of a user's preference:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100.

@@

Three versions were compared:
\begin{itemize}
\item Non Gamification. All users have the same weight.
\item Non Graph Gamification. Only experience is considered
\item Graph Gamification. Both experience and participation where considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.
